Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-08-10 ms/manuscript.Rmd
Add caption for heatmap

>>>>

**\fig \@ref(fig:heatmap)**: Variable importance scores from a full-subsets analysis using general additive models exploring the effect of climate and growth habit (terrestrial vs. epiphytic growth) on community diversity of ferns on Moorea, French Polynesia. Predictor variable abbreviations: VPD, vapor pressure deficit; SD, standard deviation. Response variable abbreviations: MPD~phy~, standard effect size (SES) of mean phylogenetic distance; MNTD~phy~, SES of mean nearest taxon distance; MPD~func~, SES of mean functional distance; MNTD~func~, SES of mean nearest functional distance; SLA, specific leaf area. All trait names refer to community-weighted mean values. Community-weighted means of frond length, frond width, stipe length, and rhizome diameter were correlated (Pearson's correlation coefficient > 0.9), so of these we only show stipe length.
